\bf An HMM-based part-of-speech tagger for Turkish

### 2015-11-15 proposal/proposal.tex
Begin working on motivation

\documentclass{article}
\usepackage{natbib}

\title{\bf Final Project Proposal}
\author{Your Name}
\date{Due date: 16 November 2015 at 11:59 PM Central time}

@@

% Lines that begin with % are comments.

\section{Motivation}
\label{sec:motivation}

Write an introductory section that motivates a particular problem you wish to solve.

This section should (at a minimum) fill the remainder of this page.

@@

Briefly survey the most salient prior work that relates to the problem you wish to solve. This section should cite relevant sources. This section should be at least one to two paragraphs in length.

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}

\title{\bf An HMM-based part-of-speech tagger for Turkish}
\author{Your Name}
\date{Due date: 16 November 2015 at 11:59 PM Central time}

@@

\section{Motivation}
\label{sec:motivation}
My main motivation for undertaking this project is to understand the main
principles underlying POS-tagging; due to time and resource constraints, it is
not possible to build a competitive POS-tagger for Turkish without doing
morphological analysis hence this project. Nevertheless, I expect my POS-tagger
to work with a decent accuracy that is good enough to be a starting point for
further development. Moreover, \citet{Korkut2015} began the development of a
Turkish NLP framework implemented in the programming language Haskell. I intend to incorporate the
POS-tagger to the Guguk project, hence contributing towards the existence of a
Turkish NLP-framework in Haskell.

@@

% Briefly survey the most salient prior work that relates to the problem you wish
% to solve. This section should cite relevant sources. This section should be at
% least one to two paragraphs in length.
The most important advancement in the computational linguistics of Turkish is
the NLP framework ``Zemberek'' by \citet{akin2007zemberek}. Although it started
out as an NLP tool for the Turkish language, Zemberek moved on to become a
framework for dealing with all Turkic languages
